Open integrated distance sampling for modelling age-structured population dynamics

### 2024-06-26 Manuscript_Nilsen_Nater.qmd
Reformatted authorship statement to CRediT

EBN Lead - Drafted the model code; Lead - Wrote first version of ms; Lead - Data collection; Contributed - Modelling and analyses

CRN Lead - Updated, further developed, and finalized model code; Lead - Modelling and analyses; Contributed - Wrote first version of ms

>>>>

**Erlend B. Nilsen**: Conceptualization, Methodology, Software, Formal analysis, Investigation, Data Curation, Writing - Original Draft, Writing - Review & Editing, Project administration, Funding acquisition.

**Chloé R. Nater**: Conceptualization, Methodology, Software, Validation, Formal analysis, Investigation, Data Curation, Writing - Original Draft, Writing - Review & Editing, Visualization.
